Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-29 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

library(needs)
needs(
  tidyverse,     # A collection of packages (e.g., ggplot2, dplyr, tidyr) for data manipulation, visualization, and general workflows.
  lubridate,     # For working with dates and times (e.g., parsing, manipulation, arithmetic).
  viridis,       # Provides colorblind-friendly color palettes for plots and visualizations.
  grid,          # A base R package for low-level grid graphics, useful for customizing complex plots.
  gridExtra,     # Extends grid by allowing multiple grid-based plots to be arranged into a single layout.
  cowplot,       # Simplifies creating publication-quality multi-panel plots, often combined with ggplot2.
  readxl,        # For reading Excel files (.xls, .xlsx) into R without requiring external dependencies.
  ARTofR,        # For applying aligned rank transform (ART) to factorial data for nonparametric analysis.
  moments,       # Provides functions to compute statistical moments (e.g., skewness, kurtosis).
  ltm,           # Used for latent trait models, including item response theory (IRT) analysis.
  sjPlot,        # A package to create publication-ready tables and visualizations for statistical models.
  kableExtra,    # Enhances the `knitr::kable()` function for producing polished and customizable tables in R Markdown.
  xtable,        # Converts R objects to LaTeX/HTML tables, especially useful for integration with Sweave/knitr.
  DescTools,     # A toolbox of descriptive statistics, effect size calculations, and data manipulation utilities.
  formattable,   # Allows creation of "formattable" data frames with customized formatting for reporting.
  psych,         # Provides tools for psychological research, including reliability analysis and descriptive statistics.
  apaTables,     # Simplifies the creation of APA-style tables for inclusion in papers or reports.
  rstatix,       # User-friendly pipe-compatible functions for common statistical tests and effect sizes.
  effsize,       # Computes effect sizes (e.g., Cohen's d) for t-tests and other statistical comparisons.
  knitr,         # Enables dynamic reporting by weaving R code and outputs into documents (e.g., R Markdown).
  papaja,        # Helps produce APA-style manuscripts directly from R Markdown.
  afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
  emmeans        # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
)

@@

# Descriptive statistics by disruption category
category_stats <- disruption_summary %>%
  group_by(Disruption_Category, Group) %>%
  summarise(
    N = n(), # Number of data points
    Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
    SD = round(sd(fixations_per_second, na.rm = TRUE), 2), # Standard deviation
    Min = round(min(fixations_per_second, na.rm = TRUE), 2), # Minimum value
    Max = round(max(fixations_per_second, na.rm = TRUE), 2), # Maximum value
    .groups = "drop"
  )

@@

##################### PLOTS ########################
##################### FIRST PLOT: FIXATION RATE OVERALL ########################

@@

# # Prepare annotation data for labels
# annotation_data <- category_stats_with_tests %>%
#   left_join(y_max_by_category, by = "Disruption_Category") %>%
#   mutate(
#     novice_label = paste0("italic(M) == ", M_Novice, " ~ ", "italic(SD) == ", SD_Novice),
#     expert_label = paste0("italic(M) == ", M_Expert, " ~ ", "italic(SD) == ", SD_Expert),
#     overall_label = paste0("italic(p) == ", p_value, " ~ ", "italic(d) == ", cohen_d)
#   )

# Create the plot
plot_category <- disruption_summary_annotated %>%
  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) + # Fixed y-axis across facets
  labs(x = "", y = "Fixations per Second") +
  ggtitle("Fixation Rate by Disruption Category\n(AOI disruptive person)") +
  scale_fill_brewer(palette = "RdBu") +
  theme_cowplot() +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 10) # Adjust facet text size if necessary
  ) 
# +
#   # Annotate novice statistics
#   geom_text(
#     data = annotation_data,
#     aes(x = 1, y = y_max, label = novice_label),
#     inherit.aes = FALSE,
#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
#   ) +
#   # Annotate expert statistics
#   geom_text(
#     data = annotation_data,
#     aes(x = 2, y = y_max, label = expert_label),
#     inherit.aes = FALSE,
#     parse = TRUE, size = 3.5, hjust = 0.5, vjust = 0
#   ) +
#   # Annotate p-value and Cohen's d
#   geom_text(
#     data = annotation_data,
#     aes(x = 1.5, y = y_max * 1.05, label = overall_label),
#     inherit.aes = FALSE,
#     parse = TRUE, size = 4, fontface = "italic", hjust = 0.5, vjust = 0
#   )

# Display the both plots
plot_overall
plot_category

@@

# Perform the repeated-measures ANOVA
anova_afex <- afex::aov_ez(
  id = "Participant", # Random effect
  dv = "fixations_per_second", # Dependent variable
  between = "Group", # Between-subject factor
  within = "Disruption_Category", # Within-subject factor
  data = anova_data
)

@@

  # Clean up category names in the contrast column
  post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast) # Replace underscores with spaces
  post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast) # Replace dots with spaces

@@

# Normality Tests (Shapiro-Wilk)
normality_tests <- df_aoi_disrup %>%
  group_by(Group) %>%
  summarise(
    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),
    .groups = "drop"
  )

# Mann-Whitney U-Test and Effect Size
mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)

# Effect Size Calculation for Mann-Whitney (r)
n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))
n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))
r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)

kable(
  mann_whitney_results,
  caption = "Mann-Whitney U-Test Results for Disruption Duration",
  row.names = FALSE
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Kruskal-Wallis Test and Pairwise Comparisons
kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)

# Pairwise Wilcoxon test with Bonferroni correction
pairwise_wilcox <- pairwise.wilcox.test(
  x = df_aoi_disrup$Duration_of_interval_sec,
  g = df_aoi_disrup$Disruption_Category,
  p.adjust.method = "bonferroni"
)

@@

@@

# Step 2: Descriptive Statistics by Group
ttff_disrup_table <- df_ttff_disrup %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
  )

@@

# Step 3: Descriptive Statistics by Category and Group
summary_stats_category_group <- df_ttff_disrup %>%
  group_by(Disruption_Category, Group) %>%
  summarise(
    N = n(),
    Mean = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    SD = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Median = round(median(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    IQR = round(IQR(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Min = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Max = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    .groups = "drop"
  )

knitr::kable(
  summary_stats_category_group,
  caption = "Descriptive Statistics for Time to First Fixation by Category and Group",
  col.names = c("Category", "Group", "N", "Mean", "SD", "Median", "IQR", "Min", "Max"),
  row.names = FALSE
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

# Demo Data
df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(!LI06_05 %in% c(201, 223)) %>%  # Exclude participants without eye-tracking data
  transmute(
    Participant = LI06_05,
    `Teaching Experience` = LI04_01
  ) %>%
  arrange(Participant)

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Person
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  select(Participant,
        Number_fixation_min_mtu,
        Average_duration_mtu,
        GRI_mtu) %>% 
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Person
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  select(Participant,
         Stud_number_fixation_min,
         Average_duration_stud
         ) %>% 
  arrange(Participant) %>% 
  drop_na()

# ET-Measures (AOI Disruptive Person)
# Number of fixations per second and Average duration of fixations
# Define the different types of disruptions and categories
disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
                 "Drumming_with_hands", "Head_on_table", "Heckling", 
                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")

@@

# SRI Rating Data
df_sri <- read_xlsx("data/Coding_SRI.xlsx") %>%
  filter(!ID %in% c(201, 223)) %>%
  rename(Participant = ID) %>%
  group_by(Participant) %>%
  summarise(
    Disruption_appraisal = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    Confidence_appraisal = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    Prevalence_rating = round(mean(prevalence_rating, na.rm = TRUE), 2)
  ) %>% 
  arrange(Participant)

# Situational Judgment Test (SJT)
df_sjt <- read_excel("./data/SJT.xlsx") %>%
  filter(!UI06_05 %in% c(201, 223)) %>%
  transmute(
    Participant = UI06_05,
    SJT_All = SJT_KF_gek,
    SJT_Monitoring = SJT_AL_gek
  )

# Self-Evaluation Data
df_self_eval <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(!LI06_05 %in% c(201, 223)) %>%
  mutate(across(starts_with("L"), as.numeric)) %>%  # Convert all "L"-prefix columns to numeric
  transmute(
    Participant = LI06_05,
    Self_eval_classroom_management = rowMeans(select(., starts_with("LM")), na.rm = TRUE),
    Self_eval_non_paraverbal_communication = rowMeans(select(., starts_with("LP")), na.rm = TRUE),
    Self_eval_total = rowMeans(select(., starts_with("L")), na.rm = TRUE)
  )

@@

# Combine all prepared datasets
df_list <- list(
  df_demo,
  df_aoi_numb_dur,
  df_aoi_stud,
  df_aoi_disrup,
  df_sri,
  df_sjt,
  df_self_eval
)

df_merge <- reduce(df_list, full_join, by = "Participant") %>%
  select(
    GRI_mtu, SJT_All, Self_eval_total, Mean_disruption_appraisal, Mean_confidence_appraisal
  )

# 3. Correlation Analysis -----------------------------------------------

# Compute Correlation Matrix
cor_tab <- cor(df_merge, method = "pearson", use = "complete.obs") %>% round(2)

# Create APA-Style Correlation Table
apa.cor.table(
  cor_tab,
  filename = "correlation_table.docx"
)

# p-values for specific correlations
pval_gri_sjt <- cor.test(df_merge$GRI_mtu, df_merge$SJT_All)$p.value
pval_gri_self_eval <- cor.test(df_merge$GRI_mtu, df_merge$Self_eval_total)$p.value

# Print Correlation Results
print(cor_tab)
cat("P-value (GRI x SJT):", pval_gri_sjt, "\n")
cat("P-value (GRI x Self-evaluation):", pval_gri_self_eval, "\n")

>>>>

library(needs)
needs(
  tidyverse,     # A collection of packages (e.g., ggplot2, dplyr, tidyr) for data manipulation, visualization, and general workflows.
  lubridate,     # For working with dates and times (e.g., parsing, manipulation, arithmetic).
  viridis,       # Provides colorblind-friendly color palettes for plots and visualizations.
  grid,          # A base R package for low-level grid graphics, useful for customizing complex plots.
  gridExtra,     # Extends grid by allowing multiple grid-based plots to be arranged into a single layout.
  cowplot,       # Simplifies creating publication-quality multi-panel plots, often combined with ggplot2.
  readxl,        # For reading Excel files (.xls, .xlsx) into R without requiring external dependencies.
  ARTofR,        # For applying aligned rank transform (ART) to factorial data for nonparametric analysis.
  moments,       # Provides functions to compute statistical moments (e.g., skewness, kurtosis).
  ltm,           # Used for latent trait models, including item response theory (IRT) analysis.
  sjPlot,        # A package to create publication-ready tables and visualizations for statistical models.
  kableExtra,    # Enhances the `knitr::kable()` function for producing polished and customizable tables in R Markdown.
  xtable,        # Converts R objects to LaTeX/HTML tables, especially useful for integration with Sweave/knitr.
  DescTools,     # A toolbox of descriptive statistics, effect size calculations, and data manipulation utilities.
  formattable,   # Allows creation of "formattable" data frames with customized formatting for reporting.
  psych,         # Provides tools for psychological research, including reliability analysis and descriptive statistics.
  apaTables,     # Simplifies the creation of APA-style tables for inclusion in papers or reports.
  rstatix,       # User-friendly pipe-compatible functions for common statistical tests and effect sizes.
  effsize,       # Computes effect sizes (e.g., Cohen's d) for t-tests and other statistical comparisons.
  knitr,         # Enables dynamic reporting by weaving R code and outputs into documents (e.g., R Markdown).
  papaja,        # Helps produce APA-style manuscripts directly from R Markdown.
  afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
  emmeans,       # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
  corrplot       # Visualize correlation matrices in a visually appealing way.
)

@@

# Descriptive statistics by disruption category
category_stats <- disruption_summary %>%
  group_by(Disruption_Category, Group) %>%
  summarise(
    N = n_distinct(Participant), # Count unique participants
    Mean = round(mean(fixations_per_second, na.rm = TRUE), 2), # Mean fixation rate
    SD = round(sd(fixations_per_second, na.rm = TRUE), 2), # Standard deviation
    Min = round(min(fixations_per_second, na.rm = TRUE), 2), # Minimum value
    Max = round(max(fixations_per_second, na.rm = TRUE), 2), # Maximum value
    .groups = "drop"
  )

@@

##################### FIRST PLOT: FIXATION RATE OVERALL ########################

@@

# Create the plot
plot_category <- disruption_summary %>%
  ggplot(mapping = aes(x = Group, y = fixations_per_second, fill = Group)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  facet_wrap(~Disruption_Category, scales = "fixed", labeller = label_wrap_gen(width = 15)) + # Fixed y-axis across facets
  labs(x = "", y = "Fixations per Second") +
  ggtitle("Fixation Rate by Disruption Category\n(AOI Disruptive Person)") +
  scale_fill_brewer(palette = "RdBu") +
  theme_cowplot() +
  theme(
    legend.position = "none",
    strip.text = element_text(size = 10) # Adjust facet text size if necessary
  )

# Display the plots
plot_overall
plot_category

@@

# Perform the repeated-measures ANOVA
anova_afex <- afex::aov_ez(
  id = "Participant", # Random effect
  dv = "fixations_per_second", # Dependent variable
  between = "Group", # Between-subject factor
  within = "Disruption_Category", # Within-subject factor
  data = disruption_summary
)

@@

# Clean up category names in the contrast column
post_hoc_results$contrast <- gsub("_", " ", post_hoc_results$contrast)
post_hoc_results$contrast <- gsub("\\.", " ", post_hoc_results$contrast)

@@

# 1. Normality Tests (Shapiro-Wilk)
# The Shapiro-Wilk test is used to assess whether the data for each group (Novice and Expert) follows a normal distribution.
normality_tests <- df_aoi_disrup %>%
  group_by(Group) %>%  # Group data by "Group" (Novice and Expert)
  summarise(
    Shapiro_Wilk_p = round(shapiro.test(Duration_of_interval_sec)$p.value, 3),  # Perform Shapiro-Wilk test for normality and round the p-value
    .groups = "drop"  # Drop the grouping after summarizing
  )

# The p-value here is extremely small (0), which indicates that both the "Novice" and "Expert" groups deviate significantly from a normal distribution. This suggests that the data in both groups are not normally distributed, and therefore, non-parametric tests like the Mann-Whitney U test are more appropriate for analyzing differences between these groups.

# Display the Shapiro-Wilk test results in a nicely formatted table
kable(
  normality_tests,  # Table with Shapiro-Wilk p-values for each group
  caption = "Shapiro-Wilk Test for Normality by Group",  # Caption for the table
  col.names = c("Group", "Shapiro-Wilk p-value"),  # Column names
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Style the table with a striped pattern

# 2. Mann-Whitney U-Test and Effect Size
# The Mann-Whitney U test is used to compare the duration of disruption between the Novice and Expert groups
# This is a non-parametric test used when the data is not normally distributed (based on the Shapiro-Wilk test results).
mann_whitney_test <- wilcox.test(Duration_of_interval_sec ~ Group, data = df_aoi_disrup, exact = FALSE)

# Calculate Effect Size (r) for the Mann-Whitney U test
# Formula for r: r = |W - (n1 * n2 / 2)| / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)
n1 <- nrow(df_aoi_disrup %>% filter(Group == "Novice"))  # Number of Novice participants
n2 <- nrow(df_aoi_disrup %>% filter(Group == "Expert"))  # Number of Expert participants
r_effect <- abs(mann_whitney_test$statistic - (n1 * n2 / 2)) / sqrt((n1 * n2 * (n1 + n2 + 1)) / 12)

# Create a data frame with the Mann-Whitney U test results, including the test statistic, p-value, and effect size
mann_whitney_results <- data.frame(
  "Test" = "Mann-Whitney U",  # Test name
  "W" = round(mann_whitney_test$statistic, 2),  # Test statistic (W)
  "p-value" = round(mann_whitney_test$p.value, 3),  # p-value from the test
  "Effect Size (r)" = round(r_effect, 3)  # Effect size (r) rounded to 3 decimals
)

# Display the Mann-Whitney U test results in a formatted table
kable(
  mann_whitney_results,
  caption = "Mann-Whitney U-Test Results for Disruption Duration",  # Table caption
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

# 3. Kruskal-Wallis Test and Pairwise Comparisons
# The Kruskal-Wallis test is a non-parametric test to compare multiple groups (Disruption Categories) at once.
# It tests whether the distributions of disruption duration across categories are equal.
kruskal_test <- kruskal.test(Duration_of_interval_sec ~ Disruption_Category, data = df_aoi_disrup)

# Create a data frame with the Kruskal-Wallis test results, including Chi-squared statistic, degrees of freedom, and p-value
kruskal_results <- data.frame(
  "Test" = "Kruskal-Wallis",  # Test name
  "Chi-squared" = round(kruskal_test$statistic, 2),  # Chi-squared statistic from the test
  "df" = kruskal_test$parameter,  # Degrees of freedom (df)
  "p-value" = round(kruskal_test$p.value, 3)  # p-value from the test
)

# Display the Kruskal-Wallis test results in a formatted table
kable(
  kruskal_results,
  caption = "Kruskal-Wallis Test Results for Differences Between Disruption Categories",  # Table caption
  row.names = FALSE  # Don't show row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

# 4. Pairwise Wilcoxon test with Bonferroni correction
# The pairwise Wilcoxon test is a non-parametric test used for multiple comparisons between pairs of disruption categories.
# The p-values are adjusted for multiple comparisons using the Bonferroni correction to control for type I error.
pairwise_wilcox <- pairwise.wilcox.test(
  x = df_aoi_disrup$Duration_of_interval_sec,  # The dependent variable (Duration of Interval)
  g = df_aoi_disrup$Disruption_Category,  # The grouping factor (Disruption Category)
  p.adjust.method = "bonferroni"  # Adjust p-values using the Bonferroni method
)

# Extract the p-values from the pairwise Wilcoxon test results and round to 3 decimal places
pairwise_results <- as.data.frame(pairwise_wilcox$p.value) %>%
  mutate(across(everything(), ~ round(., 3)))  # Round p-values to 3 decimals

# Display the pairwise Wilcoxon test results (with Bonferroni correction) in a formatted table
kable(
  pairwise_results,
  caption = "Pairwise Wilcoxon Test Results (Bonferroni Corrected)",  # Table caption
  row.names = TRUE  # Display row names
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)  # Apply striped styling to the table

@@

# Summarize the Disrup_time_fixation_sec by Participant
df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
  group_by(Participant, Group) %>%
  summarise(
    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
    .groups = "drop"
  )

@@

# Step 2: Descriptive Statistics by Group
ttff_disrup_table <- df_ttff_disrup_participant_summary %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in sec" = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "SD in sec" = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "Min in sec" = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    "Max in sec" = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2)
  )

@@

# Step 3: Descriptive Statistics by Category and Group
summary_stats_category_group <- df_ttff_disrup %>%
  group_by(Disruption_Category, Group) %>%
  summarise(
    N = n_distinct(Participant),  # Count unique participants
    Mean = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    SD = round(sd(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Median = round(median(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    IQR = round(IQR(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Min = round(min(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    Max = round(max(Disrup_time_fixation_sec, na.rm = TRUE), 2),
    .groups = "drop"
  )

# Display the table
knitr::kable(
  summary_stats_category_group,
  caption = "Descriptive Statistics for Time to First Fixation by Category and Group",
  col.names = c("Category", "Group", "N (Participants)", "Mean", "SD", "Median", "IQR", "Min", "Max"), # Ensure the column names match
  row.names = FALSE
) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

# Demo Data --------------------------------------------
df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(!LI06_05 %in% c(201, 223)) %>%  # Exclude participants without eye-tracking data
  transmute(
    Participant = LI06_05,
    `Teaching Experience` = LI04_01
  ) %>%
  arrange(Participant)

# ET-Measures (Micro-Teaching Unit) - Exclude Disruptive Person --------------------------------------------
df_aoi_numb_dur <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    Duration_of_interval  # Ensure this variable is included
  ) %>%
  dplyr::select(
    -contains("Disruptive_Person")  # Exclude Disruptive Person
  ) %>%
  rowwise() %>%
  transmute(
    Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Number_fixation_min_mtu = round(sum(c_across(starts_with("Number_of")), na.rm = TRUE) /
                                      Duration_of_interval_min, 0),
    Average_duration_mtu = round(sum(c_across(starts_with("Total_duration")), na.rm = TRUE) /
                                    sum(c_across(starts_with("Number_of")), na.rm = TRUE), 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, 2)
  ) %>%
  select(Participant,
        Number_fixation_min_mtu,
        Average_duration_mtu,
        GRI_mtu) %>% 
  arrange(Participant)

# ET-Measures (AOI Students) - Exclude Disruptive Person --------------------------------------------
df_aoi_stud <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select (
    Group,
    Duration_of_interval,
    Participant,
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)",
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ) %>%
  rowwise() %>%
  transmute(
    Group = as_factor(Group),
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Participant = Participant,
    Stud_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Stud_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Stud_number_fixation_min = round(Stud_number_fixation / Duration_of_interval_min, 2),
    Average_duration_stud = round(Stud_duration_fixation / Stud_number_fixation, 0)
  ) %>%
  select(Participant,
         Stud_number_fixation_min,
         Average_duration_stud
         ) %>% 
  arrange(Participant) %>% 
  drop_na()

# ET-Measures (AOI Disruptive Person) --------------------------------------------

# Number of fixations per second and Average duration of fixations --------------------------------------------
# Define the different types of disruptions and categories
disruptions <- c("Chatting_with_neighbour", "Clicking_pen", "Drawing", 
                 "Drumming_with_hands", "Head_on_table", "Heckling", 
                 "Looking_at_phone", "Snipping_with_fingers", "Whispering")
verbal_disruptions <- c("Chatting_with_neighbour", "Heckling", "Whispering")
physical_disruptions <- c("Clicking_pen", "Drumming_with_hands", "Snipping_with_fingers")
lack_of_eagerness <- c("Looking_at_phone", "Head_on_table", "Drawing")

@@

# Time to first fixation on AOI Disruptive Person --------------------------------------------
# Step 1: Data Preparation
df_ttff_disrup <- df_aoi %>%
  filter(TOI %in% c(verbal_disruptions, physical_disruptions, lack_of_eagerness)) %>%
  dplyr::select(
    Participant,
    TOI,
    Time_to_first_fixation.Disruptive_Person
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),  # Assigning Group based on Participant
    Disruption_Category = case_when(
      TOI %in% verbal_disruptions ~ "Verbal disruptions",
      TOI %in% physical_disruptions ~ "Physical disruptions",
      TOI %in% lack_of_eagerness ~ "Lack of eagerness to learn",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(Disruption_Category)) %>% # Keep only rows with valid categories
  drop_na() %>%
  filter(
    Time_to_first_fixation.Disruptive_Person > 0, # Exclude zero fixation times
    Time_to_first_fixation.Disruptive_Person <= 30000 # Cut-off at 30 seconds
  ) %>%
  mutate(
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person / 1000, 2)
  )

# Summarize the Disrup_time_fixation_sec by Participant
df_ttff_disrup_participant_summary <- df_ttff_disrup %>%
  group_by(Participant) %>%
  summarise(
    Disrup_time_fixation_sec = round(mean(Disrup_time_fixation_sec, na.rm = TRUE), 2), # Average time to first fixation per participant
    .groups = "drop"
  ) %>% 
  arrange(Participant)

# SRI Rating Data --------------------------------------------
# Data Import and Preprocessing ------------------------------------------
df_sri <- read_xlsx("data/Coding_SRI.xlsx") %>%
filter(
    !ID %in% c(201, 223),
    !disruption_appraisal %in% c(-100, -99, -88),
    !confidence_appraisal %in% c(-100, -99, -88),
    !prevalence_rating %in% c(-100, -99, -88)
  ) %>%  rename(Participant = ID) %>%
  group_by(Participant) %>%
  summarise(
    Disruption_appraisal = round(mean(disruption_appraisal, na.rm = TRUE), 2),
    Confidence_appraisal = round(mean(confidence_appraisal, na.rm = TRUE), 2),
    Prevalence_rating = round(mean(prevalence_rating, na.rm = TRUE), 2)
  ) %>% 
  arrange(Participant)

# Situational Judgment Test (SJT) --------------------------------------------
df_sjt <- read_excel("./data/SJT.xlsx") %>%
  filter(!UI06_05 %in% c(201, 223)) %>%
  transmute(
    Participant = UI06_05,
    SJT_All = round(SJT_KF_gek, 2),
    SJT_Monitoring = round(SJT_AL_gek, 2)
  ) %>%
  arrange(Participant)

# Self-Evaluation Data --------------------------------------------
# Data Import and Preparation
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
  mutate(
    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
    Participant = LI06_05  # Add new column "Participant"
  ) %>%
  arrange(Participant) %>% 
  select(
    Participant, 
    Group, 
    LM01_01:LM01_08,  # Classroom Management and Disruption Handling combined
    LP01_01:LP01_08   # Presence
  ) %>%
  rename(
    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
    CM_06 = LM01_06, CM_07 = LM01_07, CM_08 = LM01_08,  # Renaming combined columns
    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
  ) %>%
  na.omit()  # Remove NAs

# Summarize the scales to a mean per participant, rounded to 2 decimals
df_quest_summary <- df_quest %>%
  mutate(
    # Calculate mean for Classroom Management (CM)
    Self_Eval_CM = round(rowMeans(select(., starts_with("CM")), na.rm = TRUE), 2),
    # Calculate mean for Presence (P), excluding the Participant column
    Self_Eval_Presence = round(rowMeans(select(., starts_with("P"))[, -1], na.rm = TRUE), 2) # Exclude Participant column
  ) %>%
  select(Participant, Self_Eval_CM, Self_Eval_Presence) %>% # Keep Participant and means for each scale
  arrange(Participant)

@@

df_list <- list(
  df_demo,
  df_aoi_numb_dur,
  df_aoi_stud,
  df_aoi_disrup,
  df_ttff_disrup_participant_summary,
  df_sri,
  df_sjt,
  df_quest_summary
)

df_merge <- reduce(df_list, full_join, by = "Participant")

# 3. Correlation Analysis ---------------------------------------------

# Select relevant variables for correlation analysis
df_correlation <- df_merge %>%
  select(
    `Teaching Experience`, 
    Number_fixation_min_mtu, 
    Average_duration_mtu, 
    GRI_mtu, 
    Stud_number_fixation_min, 
    Average_duration_stud, 
    Disrup_fixations_per_second, 
    Disrup_average_fixations, 
    Disrup_time_fixation_sec, 
    Disruption_appraisal, 
    Confidence_appraisal, 
    SJT_All, 
    SJT_Monitoring, 
    Self_Eval_CM, 
    Self_Eval_Presence
  )

# Compute the correlation matrix
cor_matrix <- cor(df_correlation, use = "complete.obs")

# Visualize the correlation matrix
corrplot(cor_matrix, method = "circle", type = "lower", order = "hclust", tl.col = "black", tl.srt = 45)
